### 2014-04-10 patchy-selection-paper.tex
.

Now, we can obtain the first term in equation \eqref{eqn:gestalt_q}, the (outflux of families).
Define $\gamma(r_0)$ to be this outflux; 
i.e.\ the mean number of individuals per unit time that are born carrying the $B$ allele closer than $r_0$ to the original patch
but migrate to a larger distance.
Then for any point $x$ further than $r_0$ from the patch, 
the mean occupation density $q(x)$ is equal to the integral of $\gamma$ over all locations $x_0$ at distance $r_0$ from the patch,
multiplied by the mean occupation density at $x$ for migrant families beginning at at location.
This is a more precise statement of the decomposition of the equilibrium frequency from equation \eqref{eqn:gestalt_q}.
However, this integral is not tractable; if we assume that $r_0$ is small relative to $\|x\|$, then we get 
\begin{align}
    q(x) &= \int_{B(r_0)} u(y,x) \gamma(|y|) dy \\
         &\simeq \gamma(r_0) 2 (\pi r_0)^{d-1} u(0,x) .
\end{align}
Now, using equations \eqref{eqn:eqfreq} and \eqref{eqn:occupation_asymptotics}, we get that
\begin{align}
    \gamma(r_0) \simeq 
\end{align}

>>>>

Now, we can obtain the first term in equation \eqref{eqn:gestalt_q}, the (outflux of families).
Define $\gamma(r_0)$ to be this outflux; 
i.e.\ the mean number of individuals per unit time that are born carrying the $B$ allele closer than $r_0$ to the original patch
but migrate to a larger distance.
Then for any point $x$ further than $r_0$ from the patch, 
the mean occupation density $q(x)$ is equal to the integral of $\gamma$ over all locations $x_0$ at distance $r_0$ from the patch,
multiplied by the mean occupation density at $x$ for migrant families beginning at at location.
This is a more precise statement of the decomposition of the equilibrium frequency from equation \eqref{eqn:gestalt_q}:
\begin{align}
    q(x) &= \gamma(r_0) \int_{B(r_0)} u(y,x) dy,
\end{align}
so that $\gamma(r_0) = q(x) / \int_{B(r_0)} u(y,x) dy$, for any choice of $x$.
XXX Green function for BM killed on disk XXX
Now, using equations \eqref{eqn:eqfreq} and \eqref{eqn:occupation_asymptotics}, we get that
\begin{align}
    \gamma(r_0) \simeq 
\end{align}
